Exploratory data analysis

### 2023-08-18 index.qmd
reproc index for correct fig path

::: panel-tabset
```{r}
#| results: asis
fls <- list.files(here('figs'), 'skt_', full.names = F)
mos <- fls %>% 
  basename %>% 
  gsub('^skt_|\\.png', '', .) %>% 
  as.numeric() %>% 
  sort() %>% 
  month(label = T) %>% 
  as.character()
for(mo in seq_along(mos)){
  cat('## ', mos[mo], '\n\n')

@@

::: panel-tabset
```{r}
#| results: asis
#| out-width: 80%
fls <- list.files(here('figs'), 'segsum_', full.names = F) %>% 
  rev
locs <- fls %>% 
  basename %>% 
  gsub('^segsum_|\\.png', '', .)
for(loc in seq_along(locs)){
  cat('## ', locs[loc], '\n\n')

>>>>

::: panel-tabset
```{r}
#| results: asis
fls <- list.files(here('figseda'), 'skt_', full.names = F)
mos <- fls %>% 
  basename %>% 
  gsub('^skt_|\\.png', '', .) %>% 
  as.numeric() %>% 
  sort() %>% 
  month(label = T) %>% 
  as.character()
for(mo in seq_along(mos)){
  cat('## ', mos[mo], '\n\n')

@@

::: panel-tabset
```{r}
#| results: asis
#| out-width: 80%
fls <- list.files(here('figseda'), 'segsum_', full.names = F) %>% 
  rev
locs <- fls %>% 
  basename %>% 
  gsub('^segsum_|\\.png', '', .)
for(loc in seq_along(locs)){
  cat('## ', locs[loc], '\n\n')
